Topological Eulerian Synthesis of Slow Motion Periodic Videos

### 2018-02-04 Paper/paper.tex
exactly..exactly

Given the phase estimates $\phi_i$, we can now synthesize the final slow motion template by lining up the $N$ sliding windows $SW_{d}[\mb{X}(i)]$ by $\phi$.  For a template with $M$ frames, we choose a set of $M$ equally spaced angles $\theta_1, \theta_2, ..., \theta_M$ around the circle at which to sample the template.  Let $\Phi_i$ be the unwrapped phase of $\phi_i$.  Based on this, we esimate the number of periods $X(t)$ goes through as $k = (N \times \max_i(\Phi_i) / (2 \pi (N-d+1)))$.  Assuming $k$ is correct and that $\phi_i$ has a constant slope over $i$, there is a phase gap of $2 \pi k/N$ between adjacent stacked frames in each sliding window.  Thus, $SW_{d}[\mb{X}(i)]$ spans the interval $[\phi_i, \phi_i + 2\pi k d/N (\text{mod} 2 \pi)]$.  A given $\theta_j$ will potentially be contained in the intervals for many different windows, though it is unlikely to coincide exactly with any of the frames exactly, so we use linear interpolation to fill in a frame corresponding to $\theta_j$ in each window overlapping it.  We then take a pixel-wise median of all such interpolated frames, and we let that be the final frame at position $j$ in the template.  In practice, for videos which go through many periods, the gap between stacked frames within a window may be large, leading to ``ghosting'' artifacts in linear interpolation \cite{meyer2015phase}.  We thus add an additional user-defined parameter ``F'' which only includes linearly interpolated frames in the median if the frame to interpolate is at most $F$ frames away from an existing frame in the window.

>>>>

Given the phase estimates $\phi_i$, we can now synthesize the final slow motion template by lining up the $N$ sliding windows $SW_{d}[\mb{X}(i)]$ by $\phi$.  For a template with $M$ frames, we choose a set of $M$ equally spaced angles $\theta_1, \theta_2, ..., \theta_M$ around the circle at which to sample the template.  Let $\Phi_i$ be the unwrapped phase of $\phi_i$.  Based on this, we esimate the number of periods $X(t)$ goes through as $k = (N \times \max_i(\Phi_i) / (2 \pi (N-d+1)))$.  Assuming $k$ is correct and that $\phi_i$ has a constant slope over $i$, there is a phase gap of $2 \pi k/N$ between adjacent stacked frames in each sliding window.  Thus, $SW_{d}[\mb{X}(i)]$ spans the interval $[\phi_i, \phi_i + 2\pi k d/N (\text{mod} 2 \pi)]$.  A given $\theta_j$ will potentially be contained in the intervals for many different windows, though it is unlikely to coincide exactly with any of the frames in each window, so we use linear interpolation to fill in a frame corresponding to $\theta_j$ in each window overlapping it.  We then take a pixel-wise median of all such interpolated frames, and we let that be the final frame at position $j$ in the template.  In practice, for videos which go through many periods, the gap between stacked frames within a window may be large, leading to ``ghosting'' artifacts in linear interpolation \cite{meyer2015phase}.  We thus add an additional user-defined parameter ``F'' which only includes linearly interpolated frames in the median if the frame to interpolate is at most $F$ frames away from an existing frame in the window.
